---
title: "iteration_and_listcols"
author: "Alana Ferris"
date: "2022-11-07"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
set.seed(1)

knitr::opts_chunk$set(
  fig.width = 6,
  fig.asp = .6,
  out.width = "90%"
)
theme_set(theme_minimal() + theme(legend.position = "bottom"))
options(
  ggplot2.continuous.colour = "viridis",
  ggplot2.continuous.fill = "viridis"
)
scale_colour_discrete = scale_colour_viridis_d
scale_fill_discrete = scale_fill_viridis_d
```

# Lists

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```
So basically all you just did was put everything into a list; you jotted it down.

## Accessing List Items

```{r}
l$vec_numeric

l[[3]]

l[["mat"]]
```
He says if code has a dollar sign in it, pump the breaks, you messed up. Use this to pull something out of a list, but don't do it. Can also use double brackets to do this.

## For loops

Let's write a `for` loop to take the mean and sd of four samples from a normal distribution

```{r}
list_norm =
  list(
    a = rnorm(20, 5, 4),
    b = rnorm(20, -12, 3),
    c = rnorm(20, 17, .4),
    d = rnorm(20, 100, 1)
  )
```

Here is my function

```{r}
mean_and_sd = function(x) {
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
       sd = sd_x
    )
}
```

Let's try and make this work.

```{r}
mean_and_sd(list_norm[[1]])
```
Could keep doing this for 2, 3, 4, etc. And right now not saving results. So this can be a problem as sample size increases. So want to keep track of input and output in a concise way. So let's use a `for` loop instead. 

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norm[[i]])
}

output
```

`for` defines an index, "i", i starts at 1 and goes to 2,3,4 in this scenario.

## Map

```{r}
map(list_norm, mean_and_sd)
```

Advantage here is give it an input list and function without having to define the output in advance or write the `for` loop. Mapping is nice because can just change the function you want to do to your input list. Mean, median, whatever.

So what about other functions?

```{r}
map(list_norm, median)

map(list_norm, sd)
```
Map variants

```{r}
map_dbl(list_norm, median)

map_df(list_norm, mean_and_sd)

```
Still haven't saved anything so need to define the output if you want to do that. like

```{r}
output = map_df(list_norm, mean_and_sd)
```

# List Columns 

Up to this point, created a list of normal variables.

```{r}
listcol_df = 
  tibble(
    name = c("a", "b", "c", "d"), 
    norm = list_norm
  )

listcol_df[["norm"]]

map(listcol_df[["norm"]], mean_and_sd)

output = map(listcol_df[["norm"]], mean_and_sd)
```
The only rule for df is need same number of things in each column. And so now have a dataframe and showing how you can do all the same stuff as done before with this. Remember: map functions transform their input by applying a function to each element of a list or atomic vector and returning an object of the same length as the input. 

Now what if we create a new variable that keeps track of the output each time. 
We've been doing this with mutate, creating a new variable.
So can we add list cols 

```{r}
listcol_df %>% 
  mutate(
    m_sd = map(norm, mean_and_sd)
  ) %>% 
  select(-norm)
```

# What about something more realistic

```{r}
weather_df = 
  rnoaa::meteo_pull_monitors(
    c("USW00094728", "USC00519397", "USS0023B17S"),
    var = c("PRCP", "TMIN", "TMAX"), 
    date_min = "2017-01-01",
    date_max = "2017-12-31") %>%
  mutate(
    name = recode(
      id, 
      USW00094728 = "CentralPark_NY", 
      USC00519397 = "Waikiki_HA",
      USS0023B17S = "Waterhole_WA"),
    tmin = tmin / 10,
    tmax = tmax / 10) %>%
  select(name, id, everything())
```
Could collapse all the dif information for all weather stations into a weather station specific dataframe.

So let's nest within weather stations

```{r}
weather_nest_df = 
  weather_df %>% 
  nest(data = date:tmin)
```

Nest has taken all 365 days and 4 columns and collapsed down into single dataframe and now we can just put it in a column. 
So it really is a list column.

```{r}
weather_nest_df[["data"]]
```
Supposed wanted to do a regression of tmax on tmin 

```{r}
weather_nest_df[["data"]][[1]]

lm(tmax ~ tmin, data = weather_nest_df[["data"]][[1]])
```
First line says first taking out this column and then first entry of that list.
And then ran linear regression on tmax v tmin 

Let's write a short function

```{r}
weather_lm = function(df) {
  lm(tmax ~ tmin, data = df)
}

weather_lm(weather_nest_df[["data"]][[1]])

map(weather_nest_df[["data"]], weather_lm)
```
Now can map across this list of dfs the weather_lm function

Can i do this all in a tidy way?

```{r}
weather_nest_df %>% 
  mutate(
    model = map(data, weather_lm)
  )
```
Model column is a new column we are making with linear model results. 
We nested, mapped a function across list of df, but now we have a quick way to clean up the results.

## Unnesting

```{r}
weather_nest_df %>% 
  unnest(data)
```

## Napolean example, fixing bad stuff

```{r}
library(rvest)
```

```{r}
url = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber=1"

dynamite_html = read_html(url)

review_titles = 
  dynamite_html %>%
  html_nodes(".a-text-bold span") %>%
  html_text()

review_stars = 
  dynamite_html %>%
  html_nodes("#cm_cr-review_list .review-rating") %>%
  html_text() %>%
  str_extract("^\\d") %>%
  as.numeric()

review_text = 
  dynamite_html %>%
  html_nodes(".review-text-content span") %>%
  html_text() %>% 
  str_replace_all("\n", "") %>% 
  str_trim()

reviews = tibble(
  title = review_titles,
  stars = review_stars,
  text = review_text
)
```

What we did last time: 
```{r}
url_base = "https://www.amazon.com/product-reviews/B00005JNBQ/ref=cm_cr_arp_d_viewopt_rvwer?ie=UTF8&reviewerType=avp_only_reviews&sortBy=recent&pageNumber="

vec_urls = str_c(url_base, c(1, 2, 3, 4, 5))

read_page_reviews <- function(url) {
  
html = read_html(url)
  
  review_titles = 
    html %>%
    html_nodes(".a-text-bold span") %>%
    html_text()
  
  review_stars = 
    html %>%
    html_nodes("#cm_cr-review_list .review-rating") %>%
    html_text() %>%
    str_extract("^\\d") %>%
    as.numeric()
  
  review_text = 
    html %>%
    html_nodes(".review-text-content span") %>%
    html_text() %>% 
    str_replace_all("\n", "") %>% 
    str_trim() %>% 
    str_subset("The media could not be loaded.", negate = TRUE) %>% 
    str_subset("^$", negate = TRUE)
  
  tibble(
    title = review_titles,
    stars = review_stars,
    text = review_text
  )
}

dynamite_reviews = bind_rows(
  read_page_reviews(vec_urls[1]),
  read_page_reviews(vec_urls[2]),
  read_page_reviews(vec_urls[3]),
  read_page_reviews(vec_urls[4]),
  read_page_reviews(vec_urls[5])
)

dynamite_reviews

map(vec_urls, read_page_reviews)

napolean_reviews =
  tibble(
    page = 1:5,
    page_url = str_c(url_base, page)
  ) %>% 
  mutate(
    reviews = map(page_url, read_page_reviews)
  )

napolean_reviews %>% 
  select(-page_url) %>% 
  unnest(reviews)
```
