---
title: "simulations"
author: "Alana Ferris"
date: "2022-11-08"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
set.seed(1)
```

# Simulations 

The function we made in writing functions:

```{r}
sim_mean_sd = function(n, mu = 2, sigma = 3) {
  
  sim_data = tibble(
    x = rnorm(n, mean = mu, sd = sigma),
  )
  
  sim_data %>% 
    summarize(
      mu_hat = mean(x),
      sigma_hat = sd(x)
    )
}
```

How did we use this before?

```{r}
sim_mean_sd(30)
```
How can we use this now?
Let's start with a  `for` loop

```{r}
output = vector("list", 100)

for (i in 1:100) {
  output[[i]] = sim_mean_sd(30)
}

sim_results = bind_rows(output)
```

Let's use list columns instead

```{r}
sim_results_df = 
  expand_grid(
  sample_size = 30,
  iteration = 1:100
) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```
Used `expand_grid` to get columns/dfs that are the same everywhere between iterations. (?) Unnest to then be able to do other stuff to it, like the other stuff we've already learned in this course

```{r}
sim_results_df %>% 
  ggplot(aes(x = mu_hat)) + 
  geom_density()
```

```{r}
sim_results_df %>% 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter) %>% 
  summarize(
    emp_mean = mean(estimate),
    emp_sd = sd(estimate)) %>% 
  knitr::kable(digits = 3)
```
## Changing the sample size:
I need an input list with lots of sample sizes

```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df = map(sample_size, sim_mean_sd)
  ) %>% 
  unnest(estimate_df)
```

So what can we do with this? A lot 
Remember violin plots need it to be a factor, not a number i guess 

```{r}
sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin()
  
sim_results_df %>% 
  pivot_longer(
    mu_hat:sigma_hat,
    names_to = "parameter", 
    values_to = "estimate") %>% 
  group_by(parameter, sample_size) %>% 
  summarize(
    emp_mean = mean(estimate),
    emp_var = var(estimate)) %>% 
  knitr::kable(digits = 3)
```
And we can see that distribution is wider when n=30 than when n=240. Then we made a clean plot to look at some analysis of that data.

Next:

```{r}
sim_results_df = 
  expand_grid(
    sample_size = c(30, 60, 120, 240),
    true_sd = c(6, 3),
    iter = 1:1000
  ) %>% 
  mutate(
    estimate_df = 
      map2(.x = sample_size, .y = true_sd, ~sim_mean_sd(n = .x, sigma = .y))
  ) %>% 
  unnest(estimate_df)

sim_results_df %>% 
  mutate(
    sample_size = str_c("n = ", sample_size),
    sample_size = fct_inorder(sample_size)) %>% 
  ggplot(aes(x = sample_size, y = mu_hat, fill = sample_size)) + 
  geom_violin() +
  facet_grid(. ~ true_sd)
```
Have to use .x and .y 
S
